---
title: "AWESOME tidymodels"
---

A comprehensive list of resources that provide awesome information about [**tidymodels**](http://tidymodels.org/).

```{r}
#| include: false
library(dplyr)
source(here::here("data-raw/awesome_list.R"))
source(here::here("R/awesome_list.R"))
```

There is a page for each type of resource.

-   `r fontawesome::fa("book")` [**Book**](book.qmd)
-   `r fontawesome::fa("road")` [**Course**](course.qmd)... University lecture content, tutorials, and online learning such as MOOCs.
-   `r fontawesome::fa("bullhorn")` [**Post**](post.qmd)... Web articles and tweets (sayings, tips and meme) and discussions on question and answer website.
-   `r fontawesome::fa("fas fa-image")` [**Slide**](slide.qmd)
-   `r fontawesome::fa("video")` [**Video**](video.qmd)

## `r fontawesome::fa("thumbtack")` Pick up

```{r}
#| eval: true
#| echo: false
df_awesome |> 
  dplyr::filter(pickup == TRUE) |> 
  dplyr::select(!pickup) |> 
  create_awesome_df(df_users) |> 
  gt_export()
```

## `r fontawesome::fa("handshake")` Contributing

Your contributions are always welcome! If you would like to contribute to this list (please do), create an issue or send a mentions to [@u_ribo](http://twitter.com/u_ribo).

This work is licensed under the Creative Commons Attribution-NonCommercial 4.0 International License - [CC BY-NC 4.0](https://creativecommons.org/licenses/by-nc/4.0/legalcode)
